Avoiding tipping points in the management of ecological systems: a non-parametric Bayesian approach

### 2013-09-24 inst/doc/nonparametric-bayes.Rmd
writing

<!-- What do we call this?  Extrapolation uncertainty?  Pathological Uncertainty? -->
An additional source of uncertainty that has recieved less attention[^1] arises <!-- remove 'typical'? -->
when applying a dynamical model outside the range of data on which it has been
estimated.  This extrapolation uncertainty is felt most keenly in decision-theoretic
applications, as (a) exploring the potential action space typically involves considering
actions that may move the system outside the range of observed behavior, and (b) decision-theoretic
alogrithms rely not only on reasonable estimates of the expected outcomes, but depend on
the weights given to all possible outcomes [_e.g._ @Weitzman2013].

@@

@@

Given adequate observations of a system

One must consider actions or policy under which the system has not yet
been observed,

@@

Eacho of our models $f(S_t)$ must be estimated from training data, which
we simulate from the Allen model with parameters $r = $ ` r p[1]`, 
$K =$ ` r p[2]`, $C =$ ` r p[3]`, and  $\sigma_g =$ ` r sigma_g` 
for $T=$ `r Tobs$ timesteps, starting at initial condition $X_0 = $ `r Xo`. 
The training data can be seen in Figure 1.

>>>>

<!-- What do we call this?  Extrapolation uncertainty?  Pathological Uncertainty? -->

An additional source of uncertainty that has recieved less attention[^1]
arises when applying a dynamical model outside the range of data on
which it has been estimated.  This extrapolation uncertainty is felt
most keenly in decision-theoretic applications, as (a) exploring the
potential action space typically involves considering actions that
may move the system outside the range of observed behavior, and (b)
decision-theoretic alogrithms rely not only on reasonable estimates of
the expected outcomes, but depend on the weights given to all possible
outcomes [_e.g._ @Weitzman2013].

<!-- Perhaps this is a better-worded version of the above??

<!-- Integrate this into the paragraph, rather than as a footnote?? Make more consise? -->

@@

<!-- Does this belong?  Improve transitions -->

@@

@@

Eacho of our models $f(S_t)$ must be estimated from training data, which
we simulate from the Allen model with parameters $r = $ ` r p[1]`, 
$K =$ ` r p[2]`, $C =$ ` r p[3]`, and  $\sigma_g =$ ` r sigma_g` 
for $T=$ `r Tobs` timesteps, starting at initial condition $X_0 = $ `r Xo`. 
The training data can be seen in Figure 1.
